Disclosure of Product System Models in Life Cycle Assessment: Achieving Transparency and Privacy

### 2017-11-01 aggregation/agg-review.tex
comparative review?

In current practice, this model is then documented as a written report, and the report can be both critically reviewed and distributed to data users, but this process introduces significant interpretive challenges.  It also results in the model being frozen to a particular configuration or set of configurations at the time the results are generated.  If the review objectives include sensitivity of the model to parameter variations and/or alternative scenarios, then the review is limited to only the parameters and scenarios considered by the author.

@@

>>>>

The current practice of documenting the model with a written report sharply limits the ability of readers to interpret and reuse the data.  It also results in the model being frozen to a particular configuration or set of configurations at the time the results are generated.  Any review objectives involving sensitivity of the model to parameter variations and/or alternative scenarios are limited to the selections considered by the author.

@@

\subsection{Comparative Review: Formalizing Scope and System Boundary}

The disclosure of a PSM contains six elements, including three lists and three tables of sparse matrix data.  While the numeric data are required to critically evaluate and reproduce the study results, substantial information about the study design can be found in the list of background dependencies (\ref{itm:bg})and emissions (\ref{itm:em}).  These lists report all the distinct sources of environmental impacts in the model.  The cutoff flows, which are foreground nodes that have no nonzero entries in $A_f$, $A_d$, or $B_f$, report on the other hand what aspects were explicitly excluded from the model.

Together, these lists can be considered a functional definition of the study scope that can be used to conduct a qualitative comparison of multiple studies by different authors.

\subsection{Privacy and Partial Aggregation}

Partial aggregation is already used in practice to conceal private data, but the
